---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
Tests different options for formatting the delimiter, decimal mark, grouping mark and column header. Chooses the combinations that creates a data frame that make most sense, based on the assumptions:

* That data is rectangular, formatting that fail to read some of the columns are skipped
* That formatting that gives more non-character columns is more likely to be right
* That formatting that gives more total number of columns is more likely to be right
* That if having columns header gives same result, then it more likely that headers are not present

## Quick start

### Install

Dev version from GitHub.

```{r eval=FALSE}
devtools::install_github("lukas-rokka/readrGuess")
```

```{r}
library("readrGuess")
```

### Example

```{r, eval=FALSE}
read_guess(path_to_a_flat_file)
```
