---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
Tests different options for formatting the delimiter, decimal mark, grouping mark and column header. Chooses the combinations that creates a data frame that make most sense, based on the assumptions:

* That data is rectangular, formatting that fail to read some of the columns are skipped
* That formatting that gives more non-character columns is more likely to be right
* That formatting that gives more total number of columns is more likely to be right
* That if having columns header gives same result, then it more likely that headers are not present

For delimiters following are possible: tab (\\t), comma (,) and semicolon (;). As decimal mark: comma (,) and dot (.). As big number grouping mark: comma (,), dot (.) and space ( ) are tested. Column headers existence is also tested for, altogether 18 possible formatting combinations are tested. 


## Quick start

### Install

Dev version from GitHub.

```{r eval=FALSE}
devtools::install_github("lukas-rokka/readrGuess")
```

```{r}
library(readr)
library(readrGuess)


# all formatting combinations that are currently tested
delim_cases()
```

### Example

```{r}
# Create a date frame and format it into a semicolon delimited string
test_str <- readr::format_delim(
  data.frame(a=runif(1000, -100, 100), b="a", c=1, d=TRUE), 
  ";")

# read the string and guess the right formatting
read_guess(test_str)
```
